---
title: "Supplemental Material Part 2"
output:
    html_document:
      default: true
    md_document: 
      variant: gfm
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = here::here("output"),
      output_format = "all"
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

### 1) Import data

Importing the data for the analysis

```{r}

#library here uses the base of the R-project as initial directory
#JB stands for Judge Barrett
case_JB <- read.csv(here::here("data", "JudgeBarrettRTQT_R.csv"), header = TRUE)

#JJ stands for Judge Jackson
case_JJ <- read.csv(here::here("data", "JudgeJacksonRTQT_R.csv"), header = TRUE)

#LA stands for LA earthquake
case_LA <- read.csv(here::here("data", "LAearthquakeRTQT_R.csv"), header = TRUE)

#NZ stands for New Zealand earthquake
case_NZ <- read.csv(here::here("data", "NZearthquakeRTQT_R.csv"), header = TRUE)

#case_N20 <- read.csv("NBAFinals20RTQT_R.csv", header = TRUE)
case_N20 <- read.csv(here::here("data", "NBAFinals20RTQT_R.csv"), header = TRUE)

#case_N21 <- read.csv("NBAFinals21RTQT_R.csv", header = TRUE)
case_N21 <- read.csv(here::here("data", "NBAFinals21RTQT_R.csv"), header = TRUE)

```

### 2) Functions for the analysis

Import the set of functions used for the analysis from R script "functions_2.R"

```{r}

sys.source(here::here("scripts", "functions", "functions_2.R"), envir = knitr::knit_global())

```

### 3) Model for analysis

#### 3.1) Model definition

Model for the analysis of one-step information sharing process using all five emotions.

```{r}
#########################
#Model for the analysis #
#########################

library(lavaan)

#Model definition
model <- 'QT ~ a*fear 
          QT ~ b*anger
          QT ~ c*disgust
          QT ~ d*sadness
          QT ~ e*joy
          fear_qt ~ aa*QT
          anger_qt ~ bb*QT
          disgust_qt ~ cc*QT
          sadness_qt ~ dd*QT
          joy_qt ~ ee*QT
          
          #effect
          aaa := a*aa
          abb := a*bb
          acc := a*cc
          add := a*dd
          aee := a*ee
          baa := b*aa
          bbb := b*bb
          bcc := b*cc
          bdd := b*dd
          bee := b*ee
          caa := c*aa
          cbb := c*bb
          ccc := c*cc
          cdd := c*dd
          cee := c*ee
          daa := d*aa
          dbb := d*bb
          dcc := d*cc
          ddd := d*dd
          dee := d*ee
          eaa := e*aa
          ebb := e*bb
          ecc := e*cc
          edd := e*dd
          eee := e*ee'

```

#### 3.2) Global variables for analysis.

Definition of the variables used in the rest of the analysis for the size of the sample, number of repetitions (bootstrapping), and significance level.

```{r}

# Size of the sample for each case
sample <- 100

# Number of times the sample is repeated
repetitions <- 30

# Significance level
sig_lev <- 0.008

```

### 4) Emotions dynamic analysis

#### 4.1) Judge Barrett case

Analysis for the Judge Barret case.

```{r}

#QT_JB is the database obtained from retrieving quoted tweets
QT_JB <- read.csv(here::here("data", "JudgeBarrett_quoted_R.csv"), header = TRUE)

# Databases with number of samples equal to repetitions
db_JB <- create.ddbb(case_JB, QT_JB, repetitions, sample)

# Plot fot the QT pre, QT post, and RT levels (normalized)
QTRT_plot_JB <- create.QT_RT.plot(db_JB, repetitions, title="Figure SM 3: Average level of emotions JB case")

QTRT_plot_JB$QT_RT.plot
QTRT_plot_JB$dif_pre_post_Table[,1:5]

# List of model fit for each sample
model_fit_JB <- modelfit.list(db_JB, model, repetitions)

# Distribution of p-values and standard estimates
dist_pval_est.std_JB <- distribution_p_est.std(model_fit_JB, repetitions)

# Plot for the distribution of p-values and standard estimates
dist_pval_est.std_plot_JB <- distribution_p_est.std.plot(dist_pval_est.std_JB$dist_est.std,
                                                         dist_pval_est.std_JB$dist_pvalue)

# dist_pval_est.std_plot_JB$dist_est.std.plot
# dist_pval_est.std_plot_JB$dist_pvalue.plot

# Plot for model estimates
model_estimates_plot_JB <- create.model_estimates.plot(dist_pval_est.std_JB$dist_est.std,
                                                       dist_pval_est.std_JB$dist_pvalue,
                                                       significant = FALSE,
                                                       sig_level = sig_lev,
                                                       title="Figure SM 4: Effects JB case")

model_estimates_plot_JB

```

#### 4.2) Judge Jackson case

Analysis for the Judge Jackson case.

```{r}

#QT_JJ is the database obtained from retrieving quoted tweets
QT_JJ <- read.csv(here::here("data", "JudgeJackson_quoted_R.csv"), header = TRUE)

# Databases with number of samples equal to repetitions
db_JJ <- create.ddbb(case_JJ, QT_JJ, repetitions, sample)

# Plot fot the QT pre, QT post, and RT levels (normalized)
QTRT_plot_JJ <- create.QT_RT.plot(db_JJ, repetitions, title="Figure SM 5: Average level of emotions JJ case")

QTRT_plot_JJ$QT_RT.plot
QTRT_plot_JJ$dif_pre_post_Table[,1:5]

# List of model fit for each sample
model_fit_JJ <- modelfit.list(db_JJ, model, repetitions)

# Distribution of p-values and standard estimates
dist_pval_est.std_JJ <- distribution_p_est.std(model_fit_JJ, repetitions)

# Plot for the distribution of p-values and standard estimates
dist_pval_est.std_plot_JJ <- distribution_p_est.std.plot(dist_pval_est.std_JJ$dist_est.std,
                                                         dist_pval_est.std_JJ$dist_pvalue)

# dist_pval_est.std_plot_JJ$dist_est.std.plot
# dist_pval_est.std_plot_JJ$dist_pvalue.plot

# Plot for model estimates
model_estimates_plot_JJ <- create.model_estimates.plot(dist_pval_est.std_JJ$dist_est.std,
                                                       dist_pval_est.std_JJ$dist_pvalue,
                                                       significant = FALSE,
                                                       sig_level = sig_lev,
                                                       title="Figure SM 6: Effects JJ case")
model_estimates_plot_JJ

```

#### 4.3) LA case

Analysis for the Los Angeles earthquake case.

```{r}

#QT_LA is the database obtained from retrieving quoted tweets
QT_LA <- read.csv(here::here("data", "LAearthquake_quoted_R.csv"), header = TRUE)

# Databases with number of samples equal to repetitions
db_LA <- create.ddbb(case_LA, QT_LA, repetitions, n_sample = 150)

# Plot fot the QT pre, QT post, and RT levels (normalized)
QTRT_plot_LA <- create.QT_RT.plot(db_LA, repetitions, title="Figure SM 7: Average level of emotions LA case")

QTRT_plot_LA$QT_RT.plot
QTRT_plot_LA$dif_pre_post_Table[,1:5]

# List of model fit for each sample
model_fit_LA <- modelfit.list(db_LA, model, repetitions)

# Distribution of p-values and standard estimates
dist_pval_est.std_LA <- distribution_p_est.std(model_fit_LA, repetitions)

# Plot for the distribution of p-values and standard estimates
dist_pval_est.std_plot_LA <- distribution_p_est.std.plot(dist_pval_est.std_LA$dist_est.std,
                                                         dist_pval_est.std_LA$dist_pvalue)

# dist_pval_est.std_plot_LA$dist_est.std.plot
# dist_pval_est.std_plot_LA$dist_pvalue.plot

# Plot for model estimates
model_estimates_plot_LA <- create.model_estimates.plot(dist_pval_est.std_LA$dist_est.std,
                                                       dist_pval_est.std_LA$dist_pvalue,
                                                       significant = FALSE,
                                                       sig_level = sig_lev,
                                                       title="Figure SM 8: Effects LA case")
model_estimates_plot_LA

```

#### 4.4) NZ case

Analysis for New Zealand earthquake case

```{r}

#QT_NZ is the database obtained from retrieving quoted tweets
QT_NZ <- read.csv(here::here("data", "NZearthquake_quoted_R.csv"), header = TRUE)

# Databases with number of samples equal to repetitions
db_NZ <- create.ddbb(case_NZ, QT_NZ, repetitions, n_sample = 50)
#(case_ddbb, ddbb_QT, n_repetitions, n_sample)

# Plot fot the QT pre, QT post, and RT levels (normalized)
QTRT_plot_NZ <- create.QT_RT.plot(db_NZ, repetitions, title="Figure SM 9: Average level of emotions NZ case")

QTRT_plot_NZ$QT_RT.plot
QTRT_plot_NZ$dif_pre_post_Table[,1:5]

# List of model fit for each sample
model_fit_NZ <- modelfit.list(db_NZ, model, repetitions)

# Distribution of p-values and standard estimates
dist_pval_est.std_NZ <- distribution_p_est.std(model_fit_NZ, repetitions)

# Plot for the distribution of p-values and standard estimates
dist_pval_est.std_plot_NZ <- distribution_p_est.std.plot(dist_pval_est.std_NZ$dist_est.std,
                                                         dist_pval_est.std_NZ$dist_pvalue)

# dist_pval_est.std_plot_NZ$dist_est.std.plot
# dist_pval_est.std_plot_NZ$dist_pvalue.plot

# Plot for model estimates
model_estimates_plot_NZ <- create.model_estimates.plot(dist_pval_est.std_NZ$dist_est.std,
                                                       dist_pval_est.std_NZ$dist_pvalue,
                                                       significant = FALSE,
                                                       sig_level = sig_lev,
                                                       title="Figure SM 10: Effects NZ case")
model_estimates_plot_NZ

```

#### 4.5) N20 case

Analysis for the NBA finals 2020 case

```{r}

#QT_N20 is the database obtained from retrieving quoted tweets
QT_N20 <- read.csv(here::here("data", "NBAFinals20_quoted_R.csv"), header = TRUE)

# Databases with number of samples equal to repetitions
db_N20 <- create.ddbb(case_N20, QT_N20, repetitions, sample)

# Plot fot the QT pre, QT post, and RT levels (normalized)
QTRT_plot_N20 <- create.QT_RT.plot(db_N20, repetitions, title="Figure SM 11: Average level of emotions N20 case")

QTRT_plot_N20$QT_RT.plot
QTRT_plot_N20$dif_pre_post_Table[,1:5]

# List of model fit for each sample
model_fit_N20 <- modelfit.list(db_N20, model, repetitions)

# Distribution of p-values and standard estimates
dist_pval_est.std_N20 <- distribution_p_est.std(model_fit_N20, repetitions)

# Plot for the distribution of p-values and standard estimates
dist_pval_est.std_plot_N20 <- distribution_p_est.std.plot(dist_pval_est.std_N20$dist_est.std,
                                                          dist_pval_est.std_N20$dist_pvalue)

# dist_pval_est.std_plot_N20$dist_est.std.plot
# dist_pval_est.std_plot_N20$dist_pvalue.plot

# Plot for model estimates
model_estimates_plot_N20 <- create.model_estimates.plot(dist_pval_est.std_N20$dist_est.std,
                                                       dist_pval_est.std_N20$dist_pvalue,
                                                       significant = FALSE,
                                                       sig_level = sig_lev,
                                                       title="Figure SM 12: Effects N20 case")
model_estimates_plot_N20

```

#### 4.6) N21 case

Analisys for the NBA finals 2021 case

```{r}

#QT_N21 is the database obtained from retrieving quoted tweets
QT_N21 <- read.csv(here::here("data", "NBAFinals21_quoted_R.csv"), header = TRUE)

# Databases with number of samples equal to repetitions
db_N21 <- create.ddbb(case_N21, QT_N21, repetitions, sample)

# Plot fot the QT pre, QT post, and RT levels (normalized)
QTRT_plot_N21 <- create.QT_RT.plot(db_N21, repetitions, title="Figure SM 13: Average level of emotions N21 case")

QTRT_plot_N21$QT_RT.plot
QTRT_plot_N21$dif_pre_post_Table[,1:5]

# List of model fit for each sample
model_fit_N21 <- modelfit.list(db_N21, model, repetitions)

# Distribution of p-values and standard estimates
dist_pval_est.std_N21 <- distribution_p_est.std(model_fit_N21, repetitions)

# Plot for the distribution of p-values and standard estimates
dist_pval_est.std_plot_N21 <- distribution_p_est.std.plot(dist_pval_est.std_N21$dist_est.std,
                                                          dist_pval_est.std_N21$dist_pvalue)

# dist_pval_est.std_plot_N21$dist_est.std.plot
# dist_pval_est.std_plot_N21$dist_pvalue.plot

# Plot for model estimates
model_estimates_plot_N21 <- create.model_estimates.plot(dist_pval_est.std_N21$dist_est.std,
                                                       dist_pval_est.std_N21$dist_pvalue,
                                                       significant = FALSE,
                                                       sig_level = sig_lev,
                                                       title="Figure SM 14: Effects N21 case")
model_estimates_plot_N21

```

### 5) Analysis by topic

#### 5.1) Political cases

Joint analysis for the group Judge Barret and Judge Jackson.

```{r}

#Database with two hearings
db_pol <- list()

for (i in 1:repetitions){
  
  db_pol[[i]] <- rbind(db_JB[[i]], db_JJ[[i]])
}


# Plot fot the QT pre, QT post, and RT levels (normalized)
QTRT_plot_pol <- create.QT_RT.plot(db_pol, repetitions, title = "(a) Politics")

#QTRT_plot_pol$QT_RT.plot
QTRT_plot_pol$dif_pre_post_Table[,1:5]

# List of model fit for each sample
model_fit_pol <- modelfit.list(db_pol, model, repetitions)

# Distribution of p-values and standard estimates
dist_pval_est.std_pol <- distribution_p_est.std(model_fit_pol, repetitions)

# Plot for the distribution of p-values and standard estimates
dist_pval_est.std_plot_pol <- distribution_p_est.std.plot(dist_pval_est.std_pol$dist_est.std,
                                                          dist_pval_est.std_pol$dist_pvalue)

# dist_pval_est.std_plot_pol$dist_est.std.plot
# dist_pval_est.std_plot_pol$dist_pvalue.plot

# Plot for model estimates
model_estimates_plot_pol <- create.model_estimates.plot(dist_pval_est.std_pol$dist_est.std,
                                                       dist_pval_est.std_pol$dist_pvalue,
                                                       significant = TRUE,
                                                       sig_level = sig_lev,
                                                       title = "(a) Politics")
# model_estimates_plot_pol

# table with model standard estimates and p value
std_estimates_pol <- data.frame(cbind(colMeans(dist_pval_est.std_pol$dist_est.std),
                                      colMeans(dist_pval_est.std_pol$dist_pvalue)))

colnames(std_estimates_pol) <- c('est.std.pol', 'p.value.pol')

```

#### 5.2) Earthquake cases

Joint analysis for the group LA earthquake and NZ earthquake.

```{r}

#Database with two earthquakes
db_etq <- list()

for (i in 1:repetitions){
  
  db_etq[[i]] <- rbind(db_LA[[i]], db_NZ[[i]])
}


# Plot fot the QT pre, QT post, and RT levels (normalized)
QTRT_plot_etq <- create.QT_RT.plot(db_etq, repetitions, title = "(b) Earthquakes")

# QTRT_plot_etq$QT_RT.plot
QTRT_plot_etq$dif_pre_post_Table[,1:5]

# List of model fit for each sample
model_fit_etq <- modelfit.list(db_etq, model, repetitions)

# Distribution of p-values and standard estimates
dist_pval_est.std_etq <- distribution_p_est.std(model_fit_etq, repetitions)

# Plot for the distribution of p-values and standard estimates
dist_pval_est.std_plot_etq <- distribution_p_est.std.plot(dist_pval_est.std_etq$dist_est.std,
                                                          dist_pval_est.std_etq$dist_pvalue)

# dist_pval_est.std_plot_etq$dist_est.std.plot
# dist_pval_est.std_plot_etq$dist_pvalue.plot

# Plot for model estimates
model_estimates_plot_etq <- create.model_estimates.plot(dist_pval_est.std_etq$dist_est.std,
                                                       dist_pval_est.std_etq$dist_pvalue,
                                                       significant = TRUE,
                                                       sig_level = sig_lev,
                                                       title = "(b) Earthquakes")
# model_estimates_plot_etq

# table with model standard estimates and p value
std_estimates_etq <- data.frame(cbind(colMeans(dist_pval_est.std_etq$dist_est.std),
                                      colMeans(dist_pval_est.std_etq$dist_pvalue)))

colnames(std_estimates_etq) <- c('est.std.etq', 'p.value.etq')

```

#### 5.3) Sport cases

Joint analysis for the group NBA finals 2020 and NBA finals 2021

```{r}

#Database with two NBA finals
db_spo <- list()

for (i in 1:repetitions){
  
  db_spo[[i]] <- rbind(db_N20[[i]], db_N21[[i]])
}


# Plot fot the QT pre, QT post, and RT levels (normalized)
QTRT_plot_spo <- create.QT_RT.plot(db_spo, repetitions, title = "(c) Sports")

# QTRT_plot_spo$QT_RT.plot
QTRT_plot_spo$dif_pre_post_Table[,1:5]

# List of model fit for each sample
model_fit_spo <- modelfit.list(db_spo, model, repetitions)

# Distribution of p-values and standard estimates
dist_pval_est.std_spo <- distribution_p_est.std(model_fit_spo, repetitions)

# Plot for the distribution of p-values and standard estimates
dist_pval_est.std_plot_spo <- distribution_p_est.std.plot(dist_pval_est.std_spo$dist_est.std,
                                                          dist_pval_est.std_spo$dist_pvalue)

# dist_pval_est.std_plot_spo$dist_est.std.plot
# dist_pval_est.std_plot_spo$dist_pvalue.plot

# Plot for model estimates
model_estimates_plot_spo <- create.model_estimates.plot(dist_pval_est.std_spo$dist_est.std,
                                                       dist_pval_est.std_spo$dist_pvalue,
                                                       significant = TRUE,
                                                       sig_level = sig_lev,
                                                       title = "(c) Sports")
# model_estimates_plot_spo

# table with model standard estimates and p value
std_estimates_spo <- data.frame(cbind(colMeans(dist_pval_est.std_spo$dist_est.std),
                                      colMeans(dist_pval_est.std_spo$dist_pvalue)))

colnames(std_estimates_spo) <- c('est.std.spo', 'p.value.spo')

```

#### 5.4) Manuscript Figure 4: Significant effects of lean-forward behavior using front-door criterion.

```{r}

library(ggpubr)

ggarrange(model_estimates_plot_pol,
          model_estimates_plot_etq,
          model_estimates_plot_spo,
          ncol = 2, nrow = 2, common.legend = TRUE, legend="bottom")

#Standard estimates for SCM
SCM_table <- cbind(std_estimates_pol,std_estimates_etq,std_estimates_spo)
SCM_table

```

#### 5.5) Manuscript Figure A1: Average level of emotions for lean-back and lean-forward behaviors.

```{r}

ggarrange(QTRT_plot_pol$QT_RT.plot,
          QTRT_plot_etq$QT_RT.plot,
          QTRT_plot_spo$QT_RT.plot,
          ncol = 2, nrow = 2, common.legend = TRUE, legend="bottom")

```