---
title: "Supplemental Material Part 1"
output:
    html_document:
      default: true
    md_document:
      variant: gfm 
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = here::here("output"),
      output_format = "all"
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1) Import data

Importing the data for the analysis

```{r}

#library here uses the base of the R-project as initial directory
#JB stands for Judge Barrett
case_JB <- read.csv(here::here("data", "JudgeBarrettRTQT_R.csv"), header = TRUE)

#JJ stands for Judge Jackson
case_JJ <- read.csv(here::here("data", "JudgeJacksonRTQT_R.csv"), header = TRUE)

#LA stands for LA earthquake
case_LA <- read.csv(here::here("data", "LAearthquakeRTQT_R.csv"), header = TRUE)

#NZ stands for New Zealand earthquake
case_NZ <- read.csv(here::here("data", "NZearthquakeRTQT_R.csv"), header = TRUE)

#N20 stands for NBA 2020 finals
case_N20 <- read.csv(here::here("data", "NBAFinals20RTQT_R.csv"), header = TRUE)

#N21 stands for NBA 2021 finals
case_N21 <- read.csv(here::here("data", "NBAFinals21RTQT_R.csv"), header = TRUE)

```

### 2) Functions for the analysis

Import the set of functions used for the analysis from R script "functions_1.R"

```{r}

sys.source(here::here("scripts", "functions", "functions_1.R"), envir = knitr::knit_global())

```

### 3) Sentiment analysis

#### 3.1) Judge Barrett case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the valence of lean-back and lean-forward tweets.

```{r}

#Histogram
valence_JB <- create.valence.plot(case_JB, plot_title = "JB emotional valence")

#Descriptive statistics
psych::describeBy(case_JB$sent_score, case_JB$referenced_tweets_type)

#Test the difference in valence
t.test(data = case_JB, sent_score ~ referenced_tweets_type)

#Effect size Cohen's d
cn_va_JB <- effectsize::cohens_d(case_JB[which(case_JB$referenced_tweets_type != 'retweeted'), "sent_score"],
                                 case_JB[which(case_JB$referenced_tweets_type == 'retweeted'), "sent_score"])
cn_va_JB

```

#### 3.2) Judge Jackson case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the valence of lean-back and lean-forward tweets.

```{r}

#Histogram
valence_JJ <- create.valence.plot(case_JJ, plot_title = "JJ emotional valence")

#Descriptive statistics
psych::describeBy(case_JJ$sent_score, case_JJ$referenced_tweets_type)

#Test the difference in 
t.test(data = case_JJ, sent_score ~ referenced_tweets_type)

#Effect size Cohen's d
cn_va_JJ <- effectsize::cohens_d(case_JJ[which(case_JJ$referenced_tweets_type != 'retweeted'), "sent_score"],
                                 case_JJ[which(case_JJ$referenced_tweets_type == 'retweeted'), "sent_score"])
cn_va_JJ

```

#### 3.3) LA earthquake case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the valence of lean-back and lean-forward tweets.

```{r}

#Histogram
valence_LA <- create.valence.plot(case_LA, plot_title = "LA emotional valence")

#Descriptive statistics
psych::describeBy(case_LA$sent_score, case_LA$referenced_tweets_type)

#Test the difference in 
t.test(data = case_LA, sent_score ~ referenced_tweets_type)

#Effect size Cohen's d
cn_va_LA <- effectsize::cohens_d(case_LA[which(case_LA$referenced_tweets_type != 'retweeted'), "sent_score"],
                                 case_LA[which(case_LA$referenced_tweets_type == 'retweeted'), "sent_score"])
cn_va_LA

```

#### 3.4) NZ earthquake case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the valence of lean-back and lean-forward tweets.

```{r}

#Histogram
valence_NZ <- create.valence.plot(case_NZ, plot_title = "NZ emotional valence")

#Descriptive statistics
psych::describeBy(case_NZ$sent_score, case_NZ$referenced_tweets_type)

#Test the difference in 
t.test(data = case_NZ, sent_score ~ referenced_tweets_type)

#Effect size Cohen's d
cn_va_NZ <- effectsize::cohens_d(case_NZ[which(case_NZ$referenced_tweets_type != 'retweeted'), "sent_score"],
                                 case_NZ[which(case_NZ$referenced_tweets_type == 'retweeted'), "sent_score"])
cn_va_NZ

```

#### 3.5) NBA 2020 finals case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the valence of lean-back and lean-forward tweets.

```{r}

#Histogram
valence_N20 <- create.valence.plot(case_N20, plot_title = "N20 emotional valence")

#Descriptive statistics
psych::describeBy(case_N20$sent_score, case_N20$referenced_tweets_type)

#Test the difference in 
t.test(data = case_N20, sent_score ~ referenced_tweets_type)

#Effect size Cohen's d
cn_va_N20 <- effectsize::cohens_d(case_N20[which(case_N20$referenced_tweets_type != 'retweeted'), "sent_score"],
                                  case_N20[which(case_N20$referenced_tweets_type == 'retweeted'), "sent_score"])
cn_va_N20

```

#### 3.6) NBA 2021 finals case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the valence of lean-back and lean-forward tweets.

```{r}

#Histogram
valence_N21 <- create.valence.plot(case_N21, plot_title = "N21 emotional valence")

#Descriptive statistics
psych::describeBy(case_N21$sent_score, case_N21$referenced_tweets_type)

#Test the difference in 
t.test(data = case_N21, sent_score ~ referenced_tweets_type)

#Effect size Cohen's d
cn_va_N21 <- effectsize::cohens_d(case_N21[which(case_N21$referenced_tweets_type != 'retweeted'), "sent_score"],
                                  case_N21[which(case_N21$referenced_tweets_type == 'retweeted'), "sent_score"])
cn_va_N21

```
#### 3.7) Figure SM 1: Distribution of emotional valence

Figure with the distribution of valence for lean-back and lean-forward tweets in each case.

```{r}
#Plot of the five emotions
library(ggpubr)

ggarrange(valence_JB, valence_JJ, 
          valence_NZ, valence_LA,
          valence_N20, valence_N21,
          ncol = 2, nrow = 3, common.legend = TRUE, legend="bottom")

```

#### 3.8) Manuscript Figure 2: Cohen's d effect sizes for analysis of valence

```{r}

valence <- c(cn_va_JB$Cohens_d, cn_va_JJ$Cohens_d, cn_va_NZ$Cohens_d, #careful here with the order
             cn_va_LA$Cohens_d, cn_va_N20$Cohens_d, cn_va_N21$Cohens_d)

val_low <- c(cn_va_JB$CI_low, cn_va_JJ$CI_low, cn_va_NZ$CI_low, #careful here with the order
             cn_va_LA$CI_low, cn_va_N20$CI_low, cn_va_N21$CI_low)

val_high <- c(cn_va_JB$CI_high, cn_va_JJ$CI_high, cn_va_NZ$CI_high, #careful here with the order
              cn_va_LA$CI_high, cn_va_N20$CI_high, cn_va_N21$CI_high)

cases <- c('JB', 'JJ', 'NZ', 'LA', 'N20', 'N21')


pos_neg <- valence > 0


val_cohens <- data.frame(cases, valence, pos_neg, val_low, val_high)
val_cohens$valence <- round(as.numeric(val_cohens$valence), digits = 2)
val_cohens$val_low <- round(as.numeric(val_cohens$val_low), digits = 2)
val_cohens$val_high <- round(as.numeric(val_cohens$val_high), digits = 2)

#Definition of the order to plot stages and emotions
val_cohens$cases <- factor(val_cohens$cases, levels=c('JB', 'JJ', 'NZ', 'LA', 'N20', 'N21'))

ggplot(val_cohens, aes(x = valence, y = cases, color = pos_neg, label = valence)) +
  #geom_segment(aes(x = 0, xend = valence, yend = cases), lty=2) +
  geom_point(shape=18, size=3) +
  geom_errorbar(aes(xmin=val_low, xmax=val_high), width=.2) +
  geom_vline(xintercept = 0) +
  geom_text(nudge_y = 0.2, size = 3) +
  guides(color='none') +
  scale_colour_manual(values = c('gray60', 'black')) +
  xlim(-0.8, 0.8) +
  labs(x = expression(paste("Cohen's ", italic("d ")))) +
  theme_bw()
  

```

### 4) Emotions analysis

#### 4.1) Judge Barrett case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the emotions of lean-back and lean-forward tweets.

```{r}

#Emotions distribution plots
fear_JB <- create.emotion.plot(case_JB, emotion = "fear", plot_title = "JB fear")

anger_JB <- create.emotion.plot(case_JB, emotion = "anger", plot_title = "JB anger")

disgust_JB <- create.emotion.plot(case_JB, emotion = "disgust", plot_title = "JB disgust")

sadness_JB <- create.emotion.plot(case_JB, emotion = "sadness", plot_title = "JB sadness")

joy_JB <- create.emotion.plot(case_JB, emotion = "joy", plot_title = "JB joy")

#Descriptive statistics
psych::describeBy(case_JB[10:14], case_JB$referenced_tweets_type)

#t-test for emotions
t.test(data = case_JB, fear ~ referenced_tweets_type)
t.test(data = case_JB, anger ~ referenced_tweets_type)
t.test(data = case_JB, disgust ~ referenced_tweets_type)
t.test(data = case_JB, sadness ~ referenced_tweets_type)
t.test(data = case_JB, joy ~ referenced_tweets_type)

#Effect size Cohen's d for emotions
efsz_JB <- create.effectsize.tableplot(case_JB, plot_title = "(a) JB")
efsz_JB$effectsize.table

```

#### 4.2) Judge Jackson case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the emotions of lean-back and lean-forward tweets.

```{r}

#Emotions distribution plots
fear_JJ <- create.emotion.plot(case_JJ, emotion = "fear", plot_title = "JJ fear")

anger_JJ <- create.emotion.plot(case_JJ, emotion = "anger", plot_title = "JJ anger")

disgust_JJ <- create.emotion.plot(case_JJ, emotion = "disgust", plot_title = "JJ disgust")

sadness_JJ <- create.emotion.plot(case_JJ, emotion = "sadness", plot_title = "JJ sadness")

joy_JJ <- create.emotion.plot(case_JJ, emotion = "joy", plot_title = "JJ joy")

#Descriptive statistics
psych::describeBy(case_JJ[10:14], case_JJ$referenced_tweets_type)

#t-test for emotions
t.test(data = case_JJ, fear ~ referenced_tweets_type)
t.test(data = case_JJ, anger ~ referenced_tweets_type)
t.test(data = case_JJ, disgust ~ referenced_tweets_type)
t.test(data = case_JJ, sadness ~ referenced_tweets_type)
t.test(data = case_JJ, joy ~ referenced_tweets_type)

#Effect size Cohen's d for emotions
efsz_JJ <- create.effectsize.tableplot(case_JJ, plot_title = "(b) JJ")
efsz_JJ$effectsize.table

```

#### 4.3) LA earthquake case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the emotions of lean-back and lean-forward tweets.

```{r}

#Emotions distribution plots
fear_LA <- create.emotion.plot(case_LA, emotion = "fear", plot_title = "LA fear")

anger_LA <- create.emotion.plot(case_LA, emotion = "anger", plot_title = "LA anger")

disgust_LA <- create.emotion.plot(case_LA, emotion = "disgust", plot_title = "LA disgust")

sadness_LA <- create.emotion.plot(case_LA, emotion = "sadness", plot_title = "LA sadness")

joy_LA <- create.emotion.plot(case_LA, emotion = "joy", plot_title = "LA joy")

#Descriptive statistics
psych::describeBy(case_LA[10:14], case_LA$referenced_tweets_type)

#t-test for emotions
t.test(data = case_LA, fear ~ referenced_tweets_type)
t.test(data = case_LA, anger ~ referenced_tweets_type)
t.test(data = case_LA, disgust ~ referenced_tweets_type)
t.test(data = case_LA, sadness ~ referenced_tweets_type)
t.test(data = case_LA, joy ~ referenced_tweets_type)

#Effect size Cohen's d for emotions
efsz_LA <- create.effectsize.tableplot(case_LA, plot_title = "(c) LA")
efsz_LA$effectsize.table

```

#### 4.4) NZ earthquake case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the emotions of lean-back and lean-forward tweets.

```{r}

#Emotions distribution plots
fear_NZ <- create.emotion.plot(case_NZ, emotion = "fear", plot_title = "NZ fear")

anger_NZ <- create.emotion.plot(case_NZ, emotion = "anger", plot_title = "NZ anger")

disgust_NZ <- create.emotion.plot(case_NZ, emotion = "disgust", plot_title = "NZ disgust")

sadness_NZ <- create.emotion.plot(case_NZ, emotion = "sadness", plot_title = "NZ sadness")

joy_NZ <- create.emotion.plot(case_NZ, emotion = "joy", plot_title = "NZ joy")

#Descriptive statistics
psych::describeBy(case_NZ[10:14], case_NZ$referenced_tweets_type)

#t-test for emotions
t.test(data = case_NZ, fear ~ referenced_tweets_type)
t.test(data = case_NZ, anger ~ referenced_tweets_type)
t.test(data = case_NZ, disgust ~ referenced_tweets_type)
t.test(data = case_NZ, sadness ~ referenced_tweets_type)
t.test(data = case_NZ, joy ~ referenced_tweets_type)

#Effect size Cohen's d for emotions
efsz_NZ <- create.effectsize.tableplot(case_NZ, plot_title = "(d) NZ")
efsz_NZ$effectsize.table

```

#### 4.5) NBA 2020 finals case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the emotions of lean-back and lean-forward tweets.

```{r}

#Emotions distribution plots
fear_N20 <- create.emotion.plot(case_N20, emotion = "fear", plot_title = "N20 fear")

anger_N20 <- create.emotion.plot(case_N20, emotion = "anger", plot_title = "N20 anger")

disgust_N20 <- create.emotion.plot(case_N20, emotion = "disgust", plot_title = "N20 disgust")

sadness_N20 <- create.emotion.plot(case_N20, emotion = "sadness", plot_title = "N20 sadness")

joy_N20 <- create.emotion.plot(case_N20, emotion = "joy", plot_title = "N20 joy")

#Descriptive statistics
psych::describeBy(case_N20[10:14], case_N20$referenced_tweets_type)

#t-test for emotions
t.test(data = case_N20, fear ~ referenced_tweets_type)
t.test(data = case_N20, anger ~ referenced_tweets_type)
t.test(data = case_N20, disgust ~ referenced_tweets_type)
t.test(data = case_N20, sadness ~ referenced_tweets_type)
t.test(data = case_N20, joy ~ referenced_tweets_type)

#Effect size Cohen's d for emotions
efsz_N20 <- create.effectsize.tableplot(case_N20, plot_title = "(e) N20")
efsz_N20$effectsize.table

```

#### 4.6) NBA 2021 finals case

This analysis contains descriptive statistics, t-test, and effect sizes comparisons for the emotions of lean-back and lean-forward tweets.

```{r}

#Emotions distribution plots
fear_N21 <- create.emotion.plot(case_N21, emotion = "fear", plot_title = "N21 fear")

anger_N21 <- create.emotion.plot(case_N21, emotion = "anger", plot_title = "N21 anger")

disgust_N21 <- create.emotion.plot(case_N21, emotion = "disgust", plot_title = "N21 disgust")

sadness_N21 <- create.emotion.plot(case_N21, emotion = "sadness", plot_title = "N21 sadness")

joy_N21 <- create.emotion.plot(case_N21, emotion = "joy", plot_title = "N21 joy")

#Descriptive statistics
psych::describeBy(case_N21[10:14], case_N21$referenced_tweets_type)

#t-test for emotions
t.test(data = case_N21, fear ~ referenced_tweets_type)
t.test(data = case_N21, anger ~ referenced_tweets_type)
t.test(data = case_N21, disgust ~ referenced_tweets_type)
t.test(data = case_N21, sadness ~ referenced_tweets_type)
t.test(data = case_N21, joy ~ referenced_tweets_type)

#Effect size Cohen's d for emotions
efsz_N21 <- create.effectsize.tableplot(case_N21, plot_title = "(f) N21")
efsz_N21$effectsize.table

```

#### 4.7) Figure SM 2: Distribution of emotions by case

Figure with the distribution of emotions for lean-back and lean-forward tweets in each case.

```{r, fig.height=10, fig.width=12}

ggarrange(fear_JB, anger_JB, disgust_JB, sadness_JB, joy_JB,
          fear_JJ, anger_JJ, disgust_JJ, sadness_JJ, joy_JJ,
          fear_LA, anger_LA, disgust_LA, sadness_LA, joy_LA,
          fear_NZ, anger_NZ, disgust_NZ, sadness_NZ, joy_NZ,
          fear_N20, anger_N20, disgust_N20, sadness_N20, joy_N20,
          fear_N21, anger_N21, disgust_N21, sadness_N21, joy_N21,
          ncol = 5, nrow = 6, common.legend = TRUE, legend="bottom")

```

#### 4.8) Manuscript Figure 3: Cohen's d effect sizes for analysis of emotions

```{r, fig.height=10, fig.width=12}

ggarrange(efsz_JB$effectsize.plot, efsz_JJ$effectsize.plot,
          efsz_LA$effectsize.plot, efsz_NZ$effectsize.plot,
          efsz_N20$effectsize.plot, efsz_N21$effectsize.plot,
          ncol = 2, nrow = 3, common.legend = TRUE, legend="bottom")

```